Kvantni algebrajski učinki

### 2022-08-15 src/abstract.tex
cleaned up some todos
reworded abstract slightly

\abstract{
\begin{otherlanguage}{english}
    Quantum computation is based on many modern concepts in programming language theory,
    such as linear types, (quantum) physical phenomena, and many others.
    In this thesis I intend to focus just on these two
    and show how to use them together with \(C*\)-algebras
    to better understand how quantum programs behave.
    In particular, I will develop a simple axiom system for determining the equality of programs.

    I will first present what quantum computation even is from a mathematical standpoint,
    then I will present a theory of quantum computation based on linear types and algebraic effects.
    Later I develop a corresponding algebraic theory with linear parameters from which we extract an equational theory for our quantum programming language.
\end{otherlanguage}
}

>>>>

\abstract{
\begin{otherlanguage}{english}
    Quantum computation is based on many modern concepts in programming language theory,
    such as linear types, (quantum) physical phenomena, algebraic effects, and many others.
    In this thesis we focus just on these
    and show how to use them together with \(C*\)-algebras
    to better understand how quantum programs behave.
    In particular, we develop a simple axiom system for determining the equality of programs.

    We first present what quantum computation even is from a mathematical standpoint,
    then we present a theory of quantum computation based on linear types and algebraic effects.
    Later we develop a corresponding algebraic theory with linear parameters from which we extract an equational theory for our quantum programming language.
\end{otherlanguage}
}
